\documentclass[10pt,a4paper]{article}
\usepackage[margin=1.4cm,footskip=0.5cm]{geometry}
\usepackage{newtxtext,newtxmath}
\usepackage{titlesec}
\titlespacing{\section}{0pt}{3pt}{1pt}
\titlespacing{\subsection}{0pt}{2pt}{0pt}
\usepackage{enumitem}
\setlist{nosep,leftmargin=*,itemsep=0pt,topsep=0pt}
\usepackage{parskip}
\setlength{\parskip}{1pt}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{hyperref}
\renewcommand{\baselinestretch}{0.92}
\pagestyle{empty}

\begin{document}

% --- compact header ---
\begin{center}
{\large\textbf{CSIT6910: Independent Project Proposal}}\hfill{\small MSc in Information Technology}\\[2pt]
\rule{\textwidth}{0.3pt}\\[2pt]
\begin{multicols}{2}
\textbf{Student:} LI, Chenhao \quad \textbf{ID:} 21282663\\
\columnbreak
\textbf{Supervisor:} SONG, Yangqiu \quad\textbf{Credits:} 3
\end{multicols}
\rule{\textwidth}{0.3pt}
\end{center}

% ===================================================================
\section{Title}
% ===================================================================
{\bfseries Cross-Platform Skill Migration for DeepRefine: Porting the Reafiner Agent Loop to Claude Code and Copilot CLI with Improved Harness Fidelity}

% ===================================================================
\section{Background \& Motivation}
% ===================================================================
\texttt{DeepRefine-Skill} packages the Reafiner algorithm---an agent loop that iteratively refines knowledge graphs (KGs) through retrieval, judgement, error abduction, and KG editing---into a Cursor IDE slash command. Currently, the skill has two limitations: \textbf{(1)~Framework lock-in}---it exists only as a Cursor-specific prompt, lacking a mechanism to deploy to platforms like Claude Code or GitHub Copilot CLI; and \textbf{(2)~Limited harness fidelity}---the protocol is expressed in natural language, giving the LLM freedom to deviate from the prescribed control flow, with validation occurring only post-hoc.

This project aims to port the skill to Claude Code and Copilot CLI through a unified specification--compilation approach. Furthermore, it strengthens the harness so execution faithfully follows the Reafiner reference control flow through mechanisms like structured-output enforcement and inline validation checkpoints.

% ===================================================================
\section{Research Questions}
% ===================================================================
\begin{enumerate}[label=\textbf{RQ\arabic*},leftmargin=*]
    \item \textbf{Unified Compilation:} What abstraction (state-machine, prompts, validation, tool contracts) enables a single Reafiner specification to compile into native formats for both Claude Code and Copilot CLI without manual adaptation?
    \item \textbf{Harness Fidelity:} How effective are incremental mechanisms (deterministic k-hop expansion, structured-output enforcement, inline validation) in closing the control-flow gap between the prompt-only loop and the reference algorithm?
    \item \textbf{Behavioural Consistency:} Given identical Reafiner specifications, to what extent do execution traces diverge between frameworks, and what framework-level factors explain this divergence?
\end{enumerate}

% ===================================================================
\section{Methodology}
% ===================================================================
The system follows a single-source compilation architecture: a unified Reafiner spec is ingested by a Python compiler and emitted as native skill artefacts for each target, backed by a shared \texttt{deeprefine-core} engine. The work proceeds in four phases:

\textbf{Phase~1: Baseline Quantification (Weeks~1--3)} Deploy DeepRefine to establish reference traces. Instrument the current Cursor agent loop on a curated query set; capture compliance metrics and quantify the fidelity gap versus the paper's control flow. Output: \textbf{D1}~Gap Report.

\textbf{Phase~2: Compiler \& Harness Design (Weeks~4--6)} Design the Reafiner Skill Specification (state machine, prompts, rules, Tool Contract) and build the Skill Compiler. Implement harness improvements: deterministic expansion, structured-output enforcement, and per-step inline validation. Output: \textbf{D2}~Spec, Compiler \& Harness.

\textbf{Phase~3: Framework Adapters \& Evaluation (Weeks~7--10)} Implement adapters for Claude Code (P0) and Copilot CLI (P1). Evaluate query suites to measure: (i) step-level compliance; (ii) ablation of harness mechanisms; and (iii) inter-framework trace divergence. Output: \textbf{D3}~Skill Suite, \textbf{D4}~Evaluation Report.

\textbf{Phase~4: Synthesis \& Defence (Weeks~11--13)} Synthesise findings, write thesis, and prepare project presentation with live demonstration. Output: \textbf{D5}~Final Thesis, \textbf{D6}~Project Presentation.

% ===================================================================
\section{Timeline, Deliverables \& Grading}
% ===================================================================
\begin{table}[ht!]
\small
\begin{tabularx}{\textwidth}{@{}c|X|c@{}}
\hline
\textbf{Phase} & \textbf{Activities} & \textbf{Weeks} \\
\hline
1 & Deploy DeepRefine; instrument agent loop; quantify fidelity gap vs.~reference. & 1--3 \\
2 & Unified spec; skill compiler; three harness mechanisms; ablation setup. & 4--6 \\
3 & Claude Code (P0) \& Copilot CLI (P1) adapters; cross-platform evaluation. & 7--10 \\
4 & Synthesis; thesis writing; oral defence preparation \& live demo. & 11--13 \\
\hline
\end{tabularx}
\end{table}

\vspace{-6pt}
\begin{multicols}{2}
\textbf{Deliverables:}
\begin{itemize}
    \item D1: Baseline Gap Report;
    \item D2: Compiler \& Harness;
    \item D3: 2-Framework Suite;
    \item D4: Eval Report;
    \item D5: Thesis; D6: Defence.
\end{itemize}
\columnbreak

\textbf{Grading:}
\begin{itemize}
    \item Proposal 10\%;
    \item Mid-term (D1+D2) 15\%;
    \item Implentation \& Project demo (D3+D4) 25\%;
    \item Final report (D5) 35\%;
    \item Presentation 15\%.
\end{itemize}
\end{multicols}
\vspace{2pt}
\textbf{Workload:} 3 credits, $\sim$150 hours over 13 weeks.

\small
% ===================================================================
\section{Scope Boundaries}
% ===================================================================
\small
\textbf{In scope:} (1)~designing a unified specification and compiler architecture to port the Reafiner skill to Claude Code and Copilot CLI without manual platform adaptation; (2)~engineering harness improvements (e.g., structured-output forcing, inline validation hooks) to strictly enforce LLM adherence to the 8-step state machine; and (3)~quantitatively evaluating system-level metrics, specifically protocol compliance rates and cross-platform trace consistency.

\textbf{Out of scope:} (1)~end-to-end algorithmic evaluation of the refined Knowledge Graph's quality (e.g., benchmarking downstream QA accuracy or intrinsic edge precision/recall); (2)~modifications to the core Reafiner algorithm, knowledge-extraction heuristics, or reasoning logic, which are treated as immutable upstream dependencies; and (3)~adaptation to additional agent frameworks beyond the two specified target platforms.

\end{document}
